---
title: "Current data for 2026 DRC BDBV Outbreak"
author: "Noam Ross"
date: "`r format(Sys.time(), '%Y-%m-%dT%H:%M:%S', tz = 'Africa/Lubumbashi')`"
date-format: "YYYY-MM-DD HH:mm:ss [CAT (UTC+02:00)]"
execute:
  freeze: false
---

This page shows current data from the 2026 DRC BDBV outbreak. The data are updated automatically from the [INRB-UMIE repository](https://github.com/INRB-UMIE/BDBV2026-Data).

Only raw data from confirmed cases are shown here. There are no forecasts, or corrections for likely incomplete reporting of recent cases. For data with more context, see the [INRB-UMIE dashboard](https://inrb-umie.github.io/BDBV2026-Epidemic_Dashboard/), or [the current forecast estimates by Abbot et. al.](https://epiforecasts.io/BVDOutbreakSize/stable/summary).

<style>

</style>

```{r setup}
#| include: false

library(leaflet)
wd <- gert::git_info()$path
targets::tar_option_set(
  repository = targets::tar_repository_cas_local()
)
targets::tar_load(
  c(
    drc_bdbv_leaflet,
    last_data_update,
    case_data_csv,
    last_reported_date,
    latest_sitrep
  ),
  store = fs::path(wd, "_targets")
)
# `case_data_csv` is a standalone file target (see _targets_bdbv.R). Link to it
# by basename; the file is copied to the site root by the `resources` glob.
case_file_name <- basename(case_data_csv)
```

Last date with reported data: **`r format(last_reported_date, '%Y-%m-%d')`** (from [SitRep MVE `r sprintf('%03d', latest_sitrep$number)`-2026](`r latest_sitrep$url`),  `r format(latest_sitrep$report_date, '%Y-%m-%d')`).

Download the current case data [here](`r case_file_name`).

```{r}
#| echo: false
#| column: screen
drc_bdbv_leaflet
```
